---
title: "Untitled Draft"
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Analysis

├── DOproject.Rproj
├── R
│   ├── get_gmap.R
│   ├── get_phenocovar.R
│   ├── get_pmap.R
│   ├── get_raw_phenotypes.R
│   ├── get_rawcovar.R
│   ├── get_rawfoundergenotypes.R
│   ├── get_rawgenotypes.R
│   └── plan.R
├── _drake.R
├── data
│   ├── prepared_data
│   │   ├── dataic.rds
│   │   ├── grouped.rds
│   │   ├── phenotypes.csv
│   │   └── phenotypes.rds
│   └── raw_data
│       ├── array_id.csv
│       ├── char_review.xlsx
│       ├── covar.csv
│       ├── markers.csv
│       ├── metadata.csv
│       ├── raw_phenotype.csv
│       ├── sample_index.csv
│       └── ~$axiom8_samples.xlsx
├── doc
│   ├── manuscript.Rmd
│   └── manuscript.html
└── packages.R

## Reproducibility

<details><summary>Reproducibility receipt</summary>

```{r}
## datetime
Sys.time()

## repository
if(requireNamespace('git2r', quietly = TRUE)) {
  git2r::repository()
} else {
  c(
    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
    system2("git", args = c("remote", "-v"), stdout = TRUE)
  )
}

## session info
sessionInfo()
```

</details>
